Plant Trait Imputation

### 2024-05-07 code/L1/L1_P4_TropicalAndes_plant_imputetraits.Rmd
add code to subset dataframes to desired columns for family and genus level traits

##Retrive trait records for species using BIEN & GIFT
```{r}
# Dispersal Syndrome
Dispersal.Syndrome_families_BIEN <- BIEN_trait_traitbyfamily(family = Dispersal.Syndrome_families, trait = "dispersal syndrome")
Dispersal.Syndrome_genus_BIEN <- BIEN_trait_traitbygenus(genus = Dispersal.Syndrome_genus, trait)

@@

Fruit.Length_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.13.3")
Fruit.Length_families_GIFT <- Fruit.Length_families_GIFT[Fruit.Length_families_GIFT$family %in% Fruit.Length_families, ]
```

@@

Plant.Height_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.6.3")
Plant.Height_families_GIFT <- Plant.Height_families_GIFT[Plant.Height_families_GIFT$family %in% Plant.Height_families, ]
```

@@

Fruit.Type_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.16.1")
Fruit.Type_families_GIFT <- Fruit.Type_families_GIFT[Fruit.Type_families_GIFT$family %in% Fruit.Type_families, ]
```

@@

Growth.Form_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.2.1")
Growth.Form_families_GIFT <- Growth.Form_families_GIFT[Growth.Form_families_GIFT$family %in% Growth.Form_families, ]
```

# Set the seed for reproducibility
```{r}
set.seed(123)
```

>>>>

## Retrive trait records for species using BIEN & GIFT
```{r}
# Dispersal Syndrome
Dispersal.Syndrome_families_BIEN <- BIEN_trait_traitbyfamily(family = Dispersal.Syndrome_families, trait = "whole plant dispersal syndrome")
Dispersal.Syndrome_genus_BIEN <- BIEN_trait_traitbygenus(genus = Dispersal.Syndrome_genus, trait = "whole plant dispersal syndrome")

@@

#Error in GIFT_traits_tax(trait_IDs = "3.13.3") : None of the traits asked was available at the taxonomic level.
#Fruit.Length_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.13.3")
#Fruit.Length_families_GIFT <- Fruit.Length_families_GIFT[Fruit.Length_families_GIFT$family %in% Fruit.Length_families, ]
```

@@

#Error in GIFT_traits_tax(trait_IDs = "1.6.3") :   None of the traits asked was available at the taxonomic level.
#Plant.Height_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.6.3")
#Plant.Height_families_GIFT <- Plant.Height_families_GIFT[Plant.Height_families_GIFT$family %in% Plant.Height_families, ]
```

@@

# Error in GIFT_traits_tax(trait_IDs = "3.16.1") :   None of the traits asked was available at the taxonomic level.
#Fruit.Type_families_GIFT <- GIFT_traits_tax(trait_IDs = "3.16.1")
#Fruit.Type_families_GIFT <- Fruit.Type_families_GIFT[Fruit.Type_families_GIFT$family %in% Fruit.Type_families, ]
```

@@

# Error in GIFT_traits_tax(trait_IDs = "1.2.1") :   None of the traits asked was available at the taxonomic level.
#Growth.Form_families_GIFT <- GIFT_traits_tax(trait_IDs = "1.2.1")
#Growth.Form_families_GIFT <- Growth.Form_families_GIFT[Growth.Form_families_GIFT$family %in% Growth.Form_families, ]
```

## Combine new info with existing trait table
Make sure numeric traits match the units of existing trait table. 
To fill in gaps of missing traits, use genus level data first then family level. Add column to trait dataframe of the level of trait measurement: species, genus, family.
```{r}
# for traits to family level from BIEN, keep columns of scrubbed_family, trait_name, trait_value
Dispersal.Syndrome_families_BIEN_df <- Dispersal.Syndrome_families_BIEN[, c("scrubbed_family", "trait_name", "trait_value")]
Fruit.Length_families_BIEN_df <- Fruit.Length_families_BIEN[, c("scrubbed_family", "trait_name", "trait_value")]
Plant.Height_families_BIEN_df <- Plant.Height_families_BIEN[, c("scrubbed_family", "trait_name", "trait_value")]
Fruit.Type_families_BIEN_df <- Fruit.Type_families_BIEN[, c("scrubbed_family", "trait_name", "trait_value")]
Growth.Form_families_BIEN_df <- Growth.Form_families_BIEN[, c("scrubbed_family", "trait_name", "trait_value")]
```

```{r}
# for traits to genus level from BIEN, keep columns of scrubbed_genus, trait_name, trait_value
Dispersal.Syndrome_genus_BIEN_df <- Dispersal.Syndrome_genus_BIEN[, c("scrubbed_genus", "trait_name", "trait_value")]
Fruit.Length_genus_BIEN_df <- Fruit.Length_genus_BIEN[, c("scrubbed_genus", "trait_name", "trait_value")]
Plant.Height_genus_BIEN_df <- Plant.Height_genus_BIEN[, c("scrubbed_genus", "trait_name", "trait_value")]
Fruit.Type_genus_BIEN_df <- Fruit.Type_genus_BIEN[, c("scrubbed_genus", "trait_name", "trait_value")]
Growth.Form_genus_BIEN_df <- Growth.Form_genus_BIEN[, c("scrubbed_genus", "trait_name", "trait_value")]
```

```{r}

# Impute Traits
## Set the seed for reproducibility
```{r}
set.seed(123)
```
